\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
  \textbf{#1} \hfill #2 \\
  \textit{\small#3} \hfill \textit{\small #4}\vspace{-5pt}
}







\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\definecolor{linkblue}{rgb}{0,0,0.7} % Define the color for links
\usepackage[hidelinks]{hyperref} % Modify the hyperref settings
\hypersetup{
    colorlinks=true,
    allcolors=black,    % Default color (black)
    urlcolor=linkblue       % Color for URLs
    % linkcolor=black   % Uncomment if you want to keep internal links black
}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Samy Mostafa Shaawat} \\ \vspace{3pt}
    \small
    \href{tel:+201091539396}
    {\faMobile  \hspace{.5pt} \underline { +20 109 153 9396}}
    $|$
    \href{mailto:samy.shaawat@gmail.com}
    {\raisebox{-0.1\height}\faEnvelope \hspace{.5pt} \underline  { samy.shaawat@gmail.com}}
    $|$
    \href{https://www.linkedin.com/in/SamyShaawat}
    {\faLinkedinSquare \hspace{.5pt} \underline {My LinkedIn}}
    $|$
    \href{https://github.com/SamyShaawat}
    {\faGithub \hspace{.5pt} \underline {My GitHub}}
    $|$
    \href{https://maps.app.goo.gl/6eYDnYCmNnW4MBf79}
    {\faMapMarker \hspace{.5pt} \underline {Alexandria, Egypt}}
\end{center}


%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Egypt-Japan University of Science and Technology (E-JUST)}{Alexandria, Egypt}
      {B.Sc. in Computer Science and Engineering; {Faculty of Engineering} $|$ \textbf{GPA: 3.04}}{Sep 2019 \textbf{--} Mar 2024}
  \resumeSubHeadingListEnd

%----------- Work EXPERIENCE -----------

\section{Work Experience}
  % \vspace{3pt}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Front-end Developer Intern}{Alexandria, Egypt}
      {NTI - National Telecommunication Institute}{Oct 2023 \textbf{--} Nov 2023, Internship}
    \resumeItemListStart
    \resumeItem{Worked with HTML, CSS, and JavaScript, doing tasks on making web pages that adjust well to different devices.}
    \resumeItem{Practiced with HTML5, CSS3, and Bootstrap through practical tasks to make web pages more interactive and user-friendly.}
\resumeItemListEnd


        
    \resumeSubheading
      {Machine Learning Intern}{Alexandria, Egypt}
      {Summer Training - Under Supervision of \textbf{Dr. Marwan Torki}}{Jul 2023 \textbf{--} Sep 2023, Internship}
        \resumeItemListStart
            \resumeItem{Finished all five courses of \textbf{ Deep Learning Specialization by Coursera.}}
            \resumeItem{Successfully completed the Ultrasound Nerve Segmentation competition on Kaggle,The task was to identify nerve structures in ultrasound images of the neck. }
        \resumeItemListEnd
        
    \resumeSubheading
      {Software Engineer Intern}{Alexandria, Egypt}
      {Smart System - IT Company}{Jul 2022 \textbf{--} Sep 2022, Internship}
        \resumeItemListStart
            \resumeItem{Trained on installation, implementation and design ERD on IBM Cognos Framework Manager and learned how to use IBM Maximo - Enterprise Asset Management (EAM), and also trained on \textbf{IBM Cognos Analytics 11.0 } for data modeling and SQL-based queries.}
            \resumeItem{Collaborated with the team on analytics reports for the Holding Company of Water and Wastewater (HCWW) project}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  % \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Network Analysis of Reddit for Egyptian Community $|$ \emph{\href{https://github.com/SamyShaawat/Network-Analysis-of-the-Egyptian-Reddit-Community.git}{\underline{\color{linkblue}GitHub}}} $|$ \emph{\href{https://tinyurl.com/4fyhhbvy}{\underline{\color{linkblue}The Paper}}}}{}
      {ICINCO 2023, Rome, Italy}{Nov 2023}
    \resumeItemListStart
        \resumeItem{Conducted a comprehensive network analysis of the Egyptian Reddit community, examining 23,185 users and 105 subreddits using NetworkX and Graphml.}
        \resumeItem{Employed advanced techniques for network visualization and analysis, including degree, centrality, clustering coefficients, density, and both static and dynamic community discovery. Collaborated with colleagues \textbf{Adham Hammad, Karim Farhat, Mina Thabet}, and under the guidance of \textbf{Prof. Walid Gomaa.}}
        % \resumeItem{Revealed insights into community dynamics and user interactions, identifying key influencers and evolving patterns within the digital social structure.}
    \resumeItemListEnd

    
  \resumeSubHeadingListEnd
%----------- PROJECTS -----------
\section{Projects}
% \vspace{3pt}
\resumeSubHeadingListStart          
    \resumeSubheading
        {\textbf{Toys Shop Website} $|$ \emph{\href{https://github.com/SamyShaawat/Toys-Shop-Website}{\underline{\color{linkblue}GitHub}}}}{Jan 2023}{React - NodeJs - MySQL - ExpressJs - Sequelize}{}
            \resumeItemListStart
                \resumeItem{Developed user authentication and product search features, allowing users to register, log in, and search for products by name, brand, and price.}
            \resumeItem{Implemented product filtering, detailed product display, shopping cart management, and the ability to add new products with image upload to enhance the overall e-commerce experience.}
          \resumeItemListEnd

    \resumeSubheading
        {\textbf{Pharmacy Management System} $|$ \emph{\href{https://github.com/SamyShaawat/Pharmacy-Management-System}{\underline{\color{linkblue}GitHub}}}}{Sep 2022}{Python - Tkinter - Sqlite - Pandas}{}
            \resumeItemListStart
                \resumeItem{Developed a user-friendly desktop pharmacy inventory management application using Python and Tkinter for the graphical user interface.}
            \resumeItem{Implemented features such as adding/updating items, searching by name or company, and data import/export to Excel files, enhancing pharmacy operations efficiency.}
          \resumeItemListEnd
\resumeSubHeadingListEnd
%----------- SKILLS -----------

\section{Skills}
  % \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Technical Skills:}{ C, C++, Python, JavaScript, NodeJS, HTML, CSS, Bootstrap, SQL, Git, IBM Cognos Analytics} \\ \vspace{3pt}
        
        \textbf{Personal Skills:}{ Leadership Skills, Coordinator, Organizer, Problem Solving, Decision-maker, Flexible, Research Author} \\ \vspace{3pt} 
        
        \textbf{Languages:}{ Arabic (Native), English (Intermediate)}\\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd


%-----------Achievements-----------

\section{Achievements}
    \resumeItemListStart
                 \resumeItem{Deep Learning Specialization ,Coursera, Sep 2023}
                \resumeItem{Business Intelligence Analyst 2022 - \textbf{Mastery Award}, IBM Skills Academy, Aug 2022}
                \resumeItem{Business Intelligence Analyst 2022 - \textbf{Explorer Award} , IBM Skills Academy, Jul 2022}
                \resumeItem{{Web Development Challenger Track} {, Udacity} {, Jun 2022}  }
\resumeItemListEnd



        

    
%-----------Volunteering Work and Contests-----------
\section{Volunteering Work and Contests}

\textbf{{Organizer and Coordinator} {(2020 -- 2022)}}{}{}
    \resumeItemListStart
        \resumeItem{Lead Event Organizer, TEDx, E-JUST (2022)}
        \resumeItem{Organizer, Ana Fani, Bibliotheca Alexandrina (2021)}
        \resumeItem{Organizer, Operations Team, E-JUST (From 2020 To 2022)}
        \resumeItem{Coordinator, Model of Companies Simulation (MCS), AAST (2020)}
\resumeItemListEnd
    
    \textbf{{Mentor} {, IEEE E-JUST Student Branch}{} {(2022)}}  
    
    \textbf{{Contestant} {, ECPC, AAST} {} {(2021 and 2022)} }


    
\end{document}
